% !TEX program = xelatex

\documentclass{resume}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Tony Jin}

\basicInfo{
  \email{kavinjsir@gmail.com} \textperiodcentered\ 
  \phone{(+1)617-870-9580} \textperiodcentered\ 
  \github[Kavinjsir]{https://github.com/Kavinjsir} \textperiodcentered\
  \linkedin[Tianyi Jin]{https://www.linkedin.com/in/tianyi-j-84b223146/}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Boston University (BU)}, Boston, United States}{2021 -- Present}
\textit{Master student} in Computer Science (CS), concentrate on network, expected May 2023
\datedsubsection{\textbf{Shanghai Jiao Tong University (SJTU)}, Shanghai, China}{2014 -- 2018}
\textit{B.S.} in Software Engineering (SE)

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: TypeScript, Go, C++, Java, Python
  \item Infra Stacks: Kubernetes, Prometheus, Grafana, AWS, Terraform
  \item Dev Stacks: NodeJS, ReactJS, Webpack
\end{itemize}

\section{\faUsers\ Working Experience}
\datedsubsection{\textbf{Second Spectrum} California, America}{2019 -- 2021}
\role{DevOps Engineer}{Infra Team}
Developed an incident management system company wide.
\begin{itemize}
  \item Implemented a telemetry system to efficiently track metrics(resource usage, logs and tracing).
  \item Setup the alerting system to promote the efficiency and accuracy of emergency response.
  \item Built monitoring dashboards to easily check resources, clusters and app status.
\end{itemize}

Cost Saving
\begin{itemize}
  \item Built the alert and dashboard to monitor apps that are not necessarily taking much resources.
  \item Implemented a scheduled worker to dynamically rotating AWS Aurora RDS DB Classes based on DB utilization.
  \item Dynamically allocate resources for apps with integration of K8s Hpa and AWS Cluster Autoscaler.
\end{itemize}

Boost Up Deployment Efficiency
\begin{itemize}
  \item Standardized operations on AWS products based on IaC tools to safely and efficently build, update and provision infra.
  \item Improved the deployment platform to simplify operations on launching and terminating apps and speed up deployment process.
  \item Designed Dockerfile templates for different code base to improve building efficiency.
\end{itemize}

\datedsubsection{\textbf{Second Spectrum} California, America}{2018 -- 2019}
\role{Full Stack Engineer}{App Team}
Developed and maintained a number web services
\begin{itemize}
  \item Created a web service of video players to match NBA video chunks with moving 2D dots frames.
  \item Craeted a dashboard to dynamically display real-time video transcoding status with ReactJS.
  \item Evaluated and upgraded code with reliable dev-stack, improving code readability and maintainability.
\end{itemize}

\datedsubsection{\textbf{Morgan Stanley} Shanghai, China}{Jun 2018 -- Sep 2018}
\role{Technology Intern}{Fin Tech}
Built a clearing system for Sydney Futures Exchange(SFE)
\begin{itemize}
  \item Implemented the upstream component in the clearing system with high level security.
  \item Implemented a message queue system to safely and flexibly transform and route data.
  \item Conduct unit tests of a 90\% coverage and integration test to run smoothly on staging.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

% \section{\faHeartO\ Honors and Awards}
% \datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
% \datedline{Other awards}{2015}

% \section{\faInfo\ Miscellaneous}
% \begin{itemize}[parsep=0.5ex]
%   % \item Blog: http://your.blog.me
%   \item GitHub: https://github.com/Kavinjsir
%   \item Languages: English - Fluent, Mandarin - Native speaker
% \end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
